---
title: "Heat Load Analysis"
author: "Roberto Garay Martinez"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

This R project performs the analysis of the heat load patterns of a building

The sample data provided is a 1-year data for a multi-rise building connected to the District Heating Network in Tartu (Estonia). The data consists of hourly values of heat load, ambient temperature and solar radiation over an horizontal plane. The data sources are: GREN EESTI (heat load) and the UNIVERSITY OF TARTU (weather data)

Many inspection routines are available in this notebook. Some of them are inactive for conciseness, but can be uncomented and used by the reader.

# Initiation 

``` {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Get the working directory. This is specific to each computer. Indicates where the R project is stored locally All other file routes will be built in relation to this

``` {r initiation, include=FALSE}
WD<-getwd()

# Load libraries
{
  library(lubridate)
  library(GA)
  library(Metrics)
  library(extrafont)
  font_import()
  library(ggplot2)
  library(hrbrthemes)
  hrbrthemes::import_roboto_condensed()
}

# load functions
{
  files.source = list.files(paste(WD,
                                  "/functions",
                                  sep="")
  )
  for (i in 1:length(files.source))
  {
    source(paste(getwd(),
                 "/functions/",
                 files.source[i],sep="")
    )  
  }
  rm(files.source, i)  
}

# Load data files
{
  ## List all files
  files.data = list.files(paste(WD,
                                "/data",
                                sep="")
  )
  
  ## Select data file to load
  Dat <- files.data[1]  
}

## Read the data into a dataset
{
  Dat <- read.csv(paste(getwd(),
                        "/data/",
                        Dat,
                        sep=""),
                  sep=";")
  
  rm(files.data)
}


# formating of data frame
{
  attach(Dat)
  Dat$date<- paste(Year,
                   Month, 
                   Day_Month, 
                   Hour_Day)
  Dat$date<- as.POSIXct(Dat$date,
                        tz = "GMT",
                        "%Y %m %d %H")
  detach(Dat)
  
  STRING_date<-"date"
  VEC_vars<-c("Holiday",
              "Temperature", 
              "Solar.Irradiation", 
              "Power")
  
  
  Dat<-RG_Date_Marks (Dat,
                      STRING_date,
                      VEC_vars)
}

rm(STRING_date, VEC_vars)

# Keep record of the dataset
Dat0<-Dat

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Dat0,"Dat0.csv")
setwd(WD)
```


# Data Inspection
Execution not strictly required

``` {r data inspection}
  names(Dat)
  head(Dat)
  # tail(Dat)
  # summary(Dat)
  
  # Power vs time
  var<-"Power"
  week_list=c(1, 20)
  month_list=c()
  
  RG_inspect_data(Dat,var, week_list, month_list)
  
  # Temperature vs time
  var<-"Temperature"
  week_list=c()
  month_list=c(1,7)
  
  RG_inspect_data(Dat, var, week_list, month_list)
  
  # Solar Irradiation vs time
  var<-"Solar.Irradiation"
  week_list=c(1,20)
  month_list=c()
  
  RG_inspect_data(Dat, var, week_list, month_list)
  
  # Power vs Temperature
  var<-c("Temperature", "Power")
  week_list=c()
  month_list=c(1,4,7)
  
  RG_inspect_data(Dat, var, week_list, month_list)
  
  # Solar Irradiation vs Temperature
  var<-c("Temperature","Solar.Irradiation")
  week_list=c()
  month_list=c()
  
  RG_inspect_data(Dat, var, week_list, month_list)
  
  
  # Heat Map Hour_week/Week_year
  RG_HeatMap(Dat[,
                 c("DATE_hour_week",
                   "DATE_week_year",
                   "Power")
  ])
  
  # Summary, Power & Temperature, per month
  RG_Summary(Dat,"Power","DATE_month_year")
  RG_Summary(Dat,"Temperature","DATE_month_year")
  
  # Summary, Power & Temperature, per day of the week 
  RG_Summary(Dat,"Power","DATE_day_week")
  
  # Summary, Power & Temperature, per hour of the day
  RG_Summary(Dat,"Power","DATE_hour_day")
  # RG_Summary(Dat,"Temperature","DATE_hour_day")
  
  # Same as preceding, but only for winter months
  subset_Dat<-Dat[Dat$DATE_month_year %in% c(1, 2, 3, 11, 12),]
  RG_Summary(subset_Dat,"Power","DATE_month_year")
  RG_Summary(subset_Dat,"Temperature","DATE_month_year")
  
  RG_Summary(subset_Dat,"Power","DATE_day_week")
  
  RG_Summary(subset_Dat,"Power","DATE_hour_day")
  # RG_Summary(subset_Dat,"Temperature","DATE_hour_day")
  
  rm (month_list, var, week_list, subset_Dat)
```

## Insight

Some data is missing around week 40.
Also (from the heatmap) it seems that the initiation day of the week is shifted.

Heat load depends on outdoor temperature and solar irradiation
Main dependency on temperature (as temperature and solar irradiation are partially correlated)

There is a minimum heat load during the hot/summer months
There is a linear heat load vs temperature period in the cold/winter months
There is an intermediate period in mild/spring/autumn months

Daily periods vary due to a set of facts/schedules (building dependent)
office hours (~9-17h)
night setback (~22-23h)
weekly occupation pattern

Overall, two main patterns are identifiable.

# Resampled Data
Execution not strictly required

Resampled data to day, week and month
the function "mean" is used to ensure that the system calculates meaningful values even with some data loss

``` {r data resampling, include=FALSE}
Dat.rs.d<-RG_resample(Dat,"DATE_day_year", c("Temperature", "Solar.Irradiation", "Power"), c("mean","mean","mean"))
Dat.rs.w<-RG_resample(Dat,"DATE_week_year", c("Temperature", "Solar.Irradiation", "Power"), c("mean","mean","mean"))
Dat.rs.m<-RG_resample(Dat,"DATE_month_year", c("Temperature", "Solar.Irradiation", "Power"), c("mean","mean","mean"))
```

## Inspection of resampled data
Execution not strictly required

``` {r inspection of resampled data}
  RG_HeatMap(Dat.rs.d[,
                      c("DATE_day_week",
                        "DATE_week_year",
                        "Power")
  ])
  
  RG_inspect_data (Dat.rs.d,
                   Var_list_input=c("Temperature","Power"),
                   week_list_input=c(),
                   month_list_input=c(1,3,5,7,9,11)
  )
  
  RG_inspect_data (Dat.rs.w,
                   Var_list_input=c("Temperature","Power"),
                   week_list_input=c(),
                   month_list_input=c()
  )  
  
  RG_inspect_data (Dat.rs.m,
                   Var_list_input=c("Temperature","Power"),
                   week_list_input=c(),
                   month_list_input=c()
  )
```

## Insight

Daily averaged data allows to see the main trends (except for intra-daily issues)
There is a minimum heat load during the hot/summer months
There is a linear heat load vs temperature period in the cold/winter months
There is an intermediate period in mild/spring/autumn months

Daily periods vary due to a set of facts/schedules (building dependent)
weekly occupation pattern

In cold months, two sets of linear dependencies against temperature can be seen. Probably related to weekday / weekend patterns.

Weekly data allows to see the main trends (except for intra-daily & inter-daily issues)
There is a minimum heat load during the hot/summer months
There is a linear heat load vs temperature period in the cold/winter months
There is an intermediate period in mild/spring/autumn months

ONLY ONE linear dependency against temperature can be seen (as opposed to the information with daily data)

Monthly data provides ~the same information as weekly data, but with fewer points.


``` {r remove resampled data, include=FALSE}
rm (Dat.rs.d, Dat.rs.w, Dat.rs.m)
```

# Initial Changepoint model and outlier detection
A model is trained  for the dataset. It consist of a changepoint model segmented for each hour of the week (168 models)
Then the observations too far from the model are discarded.
This process takes in the range of 3 minutes.

``` {r changepoint model and outlier detection, include=FALSE}
# Get modelCreate a data frame with the parameters of changepoint models for each hour of the week
Changepoint_Parameters_summary<-data.frame(DATE_hour_week = sort(unique(Dat$DATE_hour_week)),
                                   slope_Temp     = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   slope_Irrad    = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   intercept      = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   minimum        = rep(NA,length(unique(Dat$DATE_hour_week))))

# Update data frame with final format
Dat$Power_fitted     <-rep(NA, dim(Dat)[1])
Dat$Power_residuals  <-rep(NA, dim(Dat)[1])
Dat$IS_Outlier       <-rep(NA, dim(Dat)[1])

#Empty dataframe for output
# will be appended in each iteration & then sorted
Dat.output <- Dat[0,]

# Subset by hour of the week
start_time <- Sys.time()

for (i in Changepoint_Parameters_summary$DATE_hour_week)
{
  Dat.subs.hw<-Dat[Dat$DATE_hour_week==i,]
  
  # Get the optimal changepoint function parameters for each subset
  # Optimal = minimum absolute error
  
  opt<-RG_Detect_Outlier_Model_Based_Ch_3P (Dat.subs.hw, 2, 50, 100)
  
  Dat.subs.hw<-opt[[1]]
  Dat.output<- rbind(Dat.output,Dat.subs.hw)
  
  Changepoint_Parameters_i<-opt[[2]]
  Changepoint_Parameters_summary[Changepoint_Parameters_summary$DATE_hour_week==i,2:5]<-Changepoint_Parameters_i
  
  
  # Control of process
  current_time <- Sys.time()
  elapsed_time <- current_time - start_time
  estimated_time <- elapsed_time *
    Changepoint_Parameters_summary$DATE_hour_week[
      length(Changepoint_Parameters_summary$DATE_hour_week)]  / i


  writeLines (paste ("Progress: ", i, " / ",
                    Changepoint_Parameters_summary$DATE_hour_week[
                     length(Changepoint_Parameters_summary$DATE_hour_week)],
                    ". elapsed time: ", elapsed_time,
                    ", estimated time: ", estimated_time,
                    sep=""))
}

# Reorder output dataframe by date
Dat<-Dat.output[order(Dat.output$DATE),]

rm(Dat.output, opt, Changepoint_Parameters_i,Dat.subs.hw, i)
rm(current_time, elapsed_time, estimated_time)

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Changepoint_Parameters_summary,"Changepoint_Parameters_summary_v1.csv")
setwd(WD)

# Keep record of the dataset
Dat1<-Dat

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Dat1,"Dat1.csv")
setwd(WD)
```

## Inspection of the changepoint model
Before discarding of outliers

``` {r inspection of the changepoint model}
Changepoint_plot_coordinates<-Changepoint_Parameters_summary

Changepoint_plot_coordinates$x1<- -50
Changepoint_plot_coordinates$y1<- Changepoint_plot_coordinates$intercept+Changepoint_plot_coordinates$slope_Temp*Changepoint_plot_coordinates$x1

Changepoint_plot_coordinates$x2<- -(Changepoint_plot_coordinates$intercept-Changepoint_plot_coordinates$minimum)/Changepoint_plot_coordinates$slope_Temp
Changepoint_plot_coordinates$y2<-  Changepoint_plot_coordinates$minimum

Changepoint_plot_coordinates$x3<-  50
Changepoint_plot_coordinates$y3<-  Changepoint_plot_coordinates$minimum

plot(c(-50,50),c(0,max (Changepoint_plot_coordinates$y1)),
     type="n",
     xlab="Temperature [C]",
     ylab="Heat Load [kWh]")

for (ni in Changepoint_plot_coordinates$DATE_hour_week)
{
  bool<-Changepoint_plot_coordinates$DATE_hour_week==ni
  varX<-c(Changepoint_plot_coordinates$x1[bool],Changepoint_plot_coordinates$x2[bool],Changepoint_plot_coordinates$x3[bool])
  varY<-c(Changepoint_plot_coordinates$y1[bool],Changepoint_plot_coordinates$y2[bool],Changepoint_plot_coordinates$y3[bool])
  
  lines (varX,varY)
}

rm(Changepoint_plot_coordinates, ni, varX, varY, bool)
```

## Insight
Overall, the same two main patterns are identified, with some specificities for each hour.

It seems that for some specific hours, a third pattern can be observed. Without heat loads for loads above ~0ºC. (This only happens sometimes, based on the genetic algorithm identification process). 

``` {r save & load workspace}
# save.image(paste(WD,"Workspace.RData",sep="/"))
# 
# WD<-getwd()
# load(paste(WD,"Workspace.RData",sep="/"))
```

# Repair dataset
The current dataset only contains observations for those timestamps where an original observation was available in the dataset.
This chunk of code generates an empty observation for every hour in between the initial and final timestamps.

The content of the observations is also updated as follows:

- IS_Outlier: TRUE/FALSE/CORRECTED (only energy is corrected)

- IS_Missing: TRUE/FALSE/CORRECTED (both energy and climate are corrected)

- Power_Corrected

Corrections are performed stepwise.

## Interpolation
<1h voids, with data available for the -1 .. 1h slot on the previous and following weeks.

``` {r fill 1h gaps, include=FALSE}
# Fill 1h voids with observations available for interpolation
  STRING_date<-"DATE"
  VEC_vars<-c("Holiday",
              "Temperature",
              "Solar.Irradiation",
              "Power",
              "Power_fitted",
              "IS_Outlier")
  VEC_repair<-c("Power")
  
  Dat<-RG_Repair_1h_double_side (Dat,STRING_date,VEC_vars,VEC_repair)
  rm(STRING_date, VEC_vars, VEC_repair)
  
# Keep record of the dataset
Dat2<-Dat

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Dat2,"Dat2.csv")
setwd(WD)
```

<5h voids, with data available for the -5 .. 5h slot on the previous and following weeks.
This is done stepwise. First 2h voids, then 3h voids,...

``` {r fill gaps < than 5 hours, include=FALSE}
# Fill 5h voids with observations available for interpolation
  STRING_date<-"DATE"
  VEC_vars<-c("Holiday",
              "Temperature",
              "Solar.Irradiation",
              "Power",
              "Power_fitted",
              "IS_Outlier")
  VEC_repair<-c("Power")
  
  num_hours_max <- 5
  for (cont_num_hours in 2:num_hours_max)
  {
    num_hours<-cont_num_hours
    for (cont_num_hour_pre in 1: num_hours)
    {
      nh_pre<-cont_num_hour_pre
      nh_post<-num_hours+1-nh_pre
      Dat<-RG_Repair_multiple_h_double_side (Dat,STRING_date,VEC_vars,VEC_repair, nh_pre, nh_post)
    }
  }
  
rm(STRING_date, VEC_vars, VEC_repair)
rm(cont_num_hour_pre, cont_num_hours, nh_post, nh_pre, num_hours, num_hours_max)

# Keep record of the dataset
Dat3<-Dat

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Dat3,"Dat3.csv")
setwd(WD)
```

## Insight

In the range of 5% of data is identified as outliers.
The data filling process are able to reconstruct 30% of the outlier data. This is mostly achieved through the 1h void filling process.

# Recalculate changepoint
Once outliers are discarded and data is (partially) repaired.
This process takes in the range of 3 minutes.

``` {r changepoint model 2, include=FALSE}
# Get modelCreate a data frame with the parameters of changepoint models for each hour of the week
Changepoint_Parameters_summary_v2<-data.frame(DATE_hour_week = sort(unique(Dat$DATE_hour_week)),
                                   slope_Temp     = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   slope_Irrad    = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   intercept      = rep(NA,length(unique(Dat$DATE_hour_week))),
                                   minimum        = rep(NA,length(unique(Dat$DATE_hour_week))))

# Define a new dataframe. Format as Dat, but data after repair (Dat_repaired)
names(Dat)[c(15:19,21)]<-"kk"
names(Dat)[20]<-"Power"
Dat<-Dat[,names(Dat)%in%names(Dat0)]

# Update data frame with final format
Dat$Power_fitted     <-rep(NA, dim(Dat)[1])
Dat$Power_residuals  <-rep(NA, dim(Dat)[1])
Dat$IS_Outlier       <-rep(NA, dim(Dat)[1])

#Empty dataframe for output
# will be appended in each iteration & then sorted
Dat.output <- Dat[0,]

# Subset by hour of the week
start_time <- Sys.time()

for (i in Changepoint_Parameters_summary_v2$DATE_hour_week)
{
  Dat.subs.hw<-Dat[Dat$DATE_hour_week==i,]
  
  # Get the optimal changepoint function parameters for each subset
  # Optimal = minimum absolute error
  
  opt<-RG_Detect_Outlier_Model_Based_Ch_3P (Dat.subs.hw, 2, 50, 100)
  
  Dat.subs.hw<-opt[[1]]
  Dat.output<- rbind(Dat.output,Dat.subs.hw)
  
  Changepoint_Parameters_i<-opt[[2]]
  Changepoint_Parameters_summary_v2[Changepoint_Parameters_summary_v2$DATE_hour_week==i,2:5]<-Changepoint_Parameters_i
  
  # Control of process
  current_time <- Sys.time()
  elapsed_time <- current_time - start_time
  estimated_time <- elapsed_time *
    Changepoint_Parameters_summary_v2$DATE_hour_week[
      length(Changepoint_Parameters_summary_v2$DATE_hour_week)]  / i


  writeLines (paste ("Progress: ", i, " / ",
                    Changepoint_Parameters_summary_v2$DATE_hour_week[
                   length(Changepoint_Parameters_summary_v2$DATE_hour_week)],
                    ". elapsed time: ", elapsed_time,
                    ", estimated time: ", estimated_time,
                    sep=""))
}

# Reorder output dataframe by date
Dat<-Dat.output[order(Dat.output$DATE),]

rm(Dat.output, opt, Changepoint_Parameters_i,Dat.subs.hw, i)
rm(current_time, elapsed_time, estimated_time)

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Changepoint_Parameters_summary_v2,"Changepoint_Parameters_summary_v2.csv")
setwd(WD)

# Keep record of the dataset
Dat4<-Dat

# Write output to file
setwd(paste(WD,"output",sep="/"))
write.csv(Dat4,"Dat4.csv")
setwd(WD)
```

## Inspection of the changepoint model
After discarding of outliers

``` {r inspection of the changepoint model 2}
Changepoint_plot_coordinates<-Changepoint_Parameters_summary_v2

Changepoint_plot_coordinates$x1<- -50
Changepoint_plot_coordinates$y1<- Changepoint_plot_coordinates$intercept+Changepoint_plot_coordinates$slope_Temp*Changepoint_plot_coordinates$x1

Changepoint_plot_coordinates$x2<- -(Changepoint_plot_coordinates$intercept-Changepoint_plot_coordinates$minimum)/Changepoint_plot_coordinates$slope_Temp
Changepoint_plot_coordinates$y2<-  Changepoint_plot_coordinates$minimum

Changepoint_plot_coordinates$x3<-  50
Changepoint_plot_coordinates$y3<-  Changepoint_plot_coordinates$minimum

plot(c(-50,50),c(0,max (Changepoint_plot_coordinates$y1)),
     type="n",
     xlab="Temperature [C]",
     ylab="Heat Load [kWh]")

for (ni in Changepoint_plot_coordinates$DATE_hour_week)
{
  bool<-Changepoint_plot_coordinates$DATE_hour_week==ni
  varX<-c(Changepoint_plot_coordinates$x1[bool],Changepoint_plot_coordinates$x2[bool],Changepoint_plot_coordinates$x3[bool])
  varY<-c(Changepoint_plot_coordinates$y1[bool],Changepoint_plot_coordinates$y2[bool],Changepoint_plot_coordinates$y3[bool])
  
  lines (varX,varY)
}

rm(Changepoint_plot_coordinates, ni, varX, varY)
```

``` {r save & load workspace 2}
save.image(paste(WD,"Workspace.RData",sep="/"))

WD<-getwd()
load(paste(WD,"Workspace.RData",sep="/"))
```

# Model statistics

``` {r model statistics}
num_outliers<-sum(Dat1$IS_Outlier)
prop_outliers<-num_outliers/dim(Dat1)[1]

num_repaired_1<-sum(Dat2$IS_Repaired)
prop_repaired_1<-num_repaired_1/num_outliers

num_repaired_2<-sum(Dat3$IS_Repaired)
prop_repaired_2<-num_repaired_2/num_outliers

plot(Dat3$Power,Dat3$Power_corrected,
     xlab="Power.original [kWh]", ylab="Power.corrected [kWh]")

plot(cumsum(Dat2$Power)/sum(Dat2$Power),
     cumsum(Dat2$Power_corrected)/sum(Dat2$Power_corrected),
     xlab="Cumulated Energy.original [kWh]", ylab="Cumulated Energy.corrected [kWh]")

Power_orig<-sum(Dat3$Power)
Power_corrected<-sum(Dat3$Power_corrected)
Power_correction<-(Power_corrected-Power_orig)/Power_orig

R2_orig<-cor(Dat1$Power_fitted,Dat1$Power)
RMSE_orig<-rmse(Dat1$Power_fitted,Dat1$Power)
MAE_orig<-mae(Dat1$Power_fitted,Dat1$Power)
Power_orig_by_hour<-aggregate(Power ~ DATE_hour_day, data=Dat1, mean)[,2]

Dat1_no_outlier<-Dat1[!Dat1$IS_Outlier,]
R2_no_outlier<-cor(Dat1_no_outlier$Power_fitted,Dat1_no_outlier$Power)
RMSE_no_outlier<-rmse(Dat1_no_outlier$Power_fitted,Dat1_no_outlier$Power)
MAE_no_outlier<-mae(Dat1_no_outlier$Power_fitted,Dat1_no_outlier$Power)
Power_no_outlier_by_hour<-aggregate(Power ~ DATE_hour_day, data=Dat1_no_outlier, mean)[,2]

Dat3_repaired<-Dat3[!Dat3$IS_Outlier-Dat3$IS_Repaired,]
R2_repaired<-cor(Dat3_repaired$Power_fitted,Dat3_repaired$Power_corrected)
RMSE_repaired<-rmse(Dat3_repaired$Power_fitted,Dat3_repaired$Power_corrected)
MAE_repaired<-mae(Dat3_repaired$Power_fitted,Dat3_repaired$Power_corrected)
Power_repaired_by_hour<-aggregate(Power_corrected ~ DATE_hour_day, data=Dat3_repaired, mean)[,2]

Dat4_no_outlier<-Dat1[!Dat4$IS_Outlier,]
R2_repaired_retrained<-cor(Dat4_no_outlier$Power_fitted,Dat4_no_outlier$Power)
RMSE_repaired_retrained<-rmse(Dat4_no_outlier$Power_fitted,Dat4_no_outlier$Power)
MAE_repaired_retrained<-mae(Dat4_no_outlier$Power_fitted,Dat4_no_outlier$Power)
Power_repaired_retrained_by_hour<-aggregate(Power ~ DATE_hour_day, data=Dat4_no_outlier, mean)[,2]


R2<-c(R2_orig, R2_no_outlier, R2_repaired, R2_repaired_retrained)
RMSE<-c(RMSE_orig, RMSE_no_outlier, RMSE_repaired, RMSE_repaired_retrained)
MAE<-c(MAE_orig, MAE_no_outlier, MAE_repaired, MAE_repaired_retrained)

legend <- c("Orig.", "Out.Rm", ".Rep", "Retr")

par(mfrow=c(1,3))
barplot(R2,     ylim=c(0,1),     names.arg=legend,     ylab="R2")
barplot(RMSE,   ylim=c(0,20),    names.arg=legend,     ylab="RMSE")
barplot(MAE,    ylim=c(0,10),    names.arg=legend,     ylab="MAE")
par(mfrow=c(1,1))

legend<- c("Original", "Outlier Removed", "Outlier Repaired", "Retrained")

plot(Power_orig_by_hour, type="n", ylab="Power, kWh", xlab="hour of the day", ylim=c(0,75))
lines(Power_orig_by_hour, col="black")
lines(Power_no_outlier_by_hour, col="red")
lines(Power_repaired_by_hour, col="green")
lines(Power_repaired_retrained_by_hour, col="blue")
legend("topright", legend, col=c("black","red","green","blue"),lty=1)


```

## Insight
(figures are dependent on the parametrization of the changepoint model identification process)

Power corrections are performed for ca 130 data points. This is a relatively small number of points. Its impact in the cumulated power curve is not relevant.

Changepoint models seem to be reasonable ways to model heat load data.
Overall, good performance metrics are achieved in all cases (R2>0.9; RMSE<15.9, MAE<10 in all cases)

Performance is slightly increased when outliers are removed. Outlier repair and model retraining does not seem to have a significant input.
